Finalised versions of normalisation and threshold

### 2020-07-16 norm_threshold4.Rmd
still cleaning folder

---
title: Screening harmonies
authors:
- name: Sayani Gupta
  affiliation: Department of Econometrics and Business Statistics, Monash University
  email: Sayani.Gupta@monash.edu

@@

# Does normalisation work?
(Show with by comparing with maximum and 
showing for similar levels)
# Does it match with the threshold?
# Should they tally with each other?

@@

| facets/x-axis     	| A_1  	| A_2  	| A_3  	| .. 	| .. 	| A_K  	|
|-----	|------	|------	|------	|----	|----	|------	|
| B_1 	| p_11 	| p_12 	| p_13 	| .. 	| .. 	| p_1K 	|
| B_2 	|      	|      	|      	|    	|    	|      	|
| B_3 	|      	|      	|      	|    	|    	|      	|
| ..  	|      	|      	|      	|    	|    	|      	|
| ..  	|      	|      	|      	|    	|    	|      	|
| B_L 	| p_L1 	| p_L2 	| p_L3 	| .. 	| .. 	| p_LK 	|

$H_{01}: p_{11} = p_{21} = \ldots = p_{L1}$  
$H_{02}: p_{12} = p_{22} = \ldots = p_{L2}$  
\vdots
$H_{0K}: p_{1K} = p_{2K} = \ldots = p_{LK}$

$m$ = $L \choose 2$ (unordered)  
$m$ = $L-1$ (ordered)

|  facets/distances	| A_1  	| A_2  	| A_3  	| .. 	| .. 	| A_K  	|
|------------------	|------	|------	|------	|----	|----	|------	|
| d_1              	| d_11 	| d_12 	| d_13 	| .. 	| .. 	| d_1K 	|
| d_2              	|      	|      	|      	|    	|    	|      	|
| d_3              	|      	|      	|      	|    	|    	|      	|
| ..               	|      	|      	|      	|    	|    	|      	|
| ..               	|      	|      	|      	|    	|    	|      	|
| d_m              	| d_m1 	| d_m2 	| d_m3 	 .. 	| .. 	| d_mK 	|

$H_{01}: d_{11} = d_{21} = \ldots = d_{m1} = 0$  
$H_{02}: d_{12} = d_{22} = \ldots = d_{m2} = 0$  
\vdots
$H_{0K}: d_{1K} = d_{2K} = \ldots = d_{mK} = 0$

 - can do ANOVA at this stage
 - interpretation of results (if interaction of levels significant when testing if means of distributions of distances are equal to zero )

| facets/max-dist 	| A_1       	| A_2       | .. 	| .. 	| A_K       	|
|-----------------	|-----------	|-----------	|-----------	|----	|----	|-----------	|
| max-dist        	| max(d_11, .., dm1) 	| max(d_12, ...d_m2) 	| .. 	| .. 	| max(d_1K,...d_mK) 	|

$H_{01}: max(d_{11}, .., d_{m1}) = 0$  
$H_{02}: max(d_{12}, ...d_{m2})  = 0$  
\vdots
$H_{0K}: max(d_{1K},...d_{mK}) = 0$

 -  normalised maximum distribution follows standardised Gumbel distribution
 -  multiple hypothesis testing problem where p-values needs to be adjusted with Fisher's combination test (preferred) or Bonferroni's correction
 - What is the test statistic for multiple hypothesis problem?

@@

<!-- paiwise percentile tests for distances. Each facet is a category with m ordered/unordered pairwise distances. We are testing if the 95th percentile of these facets are equal. If at least two of them are different, we keep the harmony pair, else remove them from the list. -->

<!-- 1st screening criterion: 95th percentile different for different facet labels -->

<!-- 2nd screening/ranking criterion: within the harmonies foir which facet levels are different, MMPD is used to rank them -->

**Assumption:** random permutation without considering ordering 
(Local)

1. Given the original sequence for $\{C_i, C_j\}$; $\{v_t: t=0, 1, 2, \dots, T-1\}$, the MMPD is computed and is represented by $MMPD_{obs}$.

3. MMPD is computed for all random permutation and is represented by $MMPD_{sample}$.

7. If  $MMPD_{obs}> MMPD_{threshold}$, then it implies the observed MMPD is 95% of the times higher than the any other random permutation of the original sequence.

Pros: Considering thresholds locally for each harmony pairs would imply that data is reshuffled only within that harmony pair and generated MMPDs are only reflection of how MMPDs are when measured between that harmony pairs only.

Cons: The threshold value is considered locally for each harmony pairs and hence it does not align the original MMPD values we get. That is, a harmony pair with lower MMPD might get selected over that with a higher MMPD. Difficult to understand but it means that although MMPD value is smaller, it is significantly different from zero.

**Assumption:** random permutation without considering ordering 
(Local)

@@

```{r}
library(readr)
signi <- read_rds("data/significant_harmonies.rds")
signi
local_thres <- c(FALSE, TRUE, TRUE, FALSE, TRUE, TRUE, TRUE, FALSE, TRUE, FALSE, FALSE, TRUE, TRUE, FALSE, FALSE, FALSE)

signi %>% select(-facet_levels, -x_levels) %>% 
  mutate(local_threshold = local_thres) %>% knitr::kable(format = "latex")

<!-- **Assumption:** random permutation considering ordering -->

<!-- Intuition? -->

<!-- Original: -->

<!-- | facets/observation     	| 1  	| 2  	| 3  	| .. 	| .. 	| n  	| -->
<!-- |-----	|------	|------	|------	|----	|----	|------	| -->
<!-- | B_1 	| x_1 	| x_2 	| x_3 	| .. 	| .. 	| x_n 	| -->
<!-- | B_2 	| y_1 	| y_2 	| y_3 	| .. 	| .. 	| y_n 	| -->
<!-- | B_3 	|      	|      	|      	|    	|    	|      	| -->
<!-- | ..  	|      	|      	|      	|    	|    	|      	| -->
<!-- | ..  	|      	|      	|      	|    	|    	|      	| -->
<!-- | B_L 	| z_1 	| z_2 	| z_3 	| .. 	| .. 	| z_n 	| -->

<!-- Unordered: Permuting across levels -->

<!-- | facets/observation     	| 1  	| 2  	| 3  	| .. 	| .. 	| n  	| -->
<!-- |-----	|------	|------	|------	|----	|----	|------	| -->
<!-- | B_1 	| y_3 	| x_2 	| z_2 	| .. 	| .. 	| y_1 	| -->
<!-- | B_2 	| x_n 	| y_2 	| x_1 	| .. 	| .. 	| z_3 	| -->
<!-- | B_3 	|      	|      	|      	|    	|    	|      	| -->
<!-- | ..  	|      	|      	|      	|    	|    	|      	| -->
<!-- | ..  	|      	|      	|      	|    	|    	|      	| -->
<!-- | B_L 	| x_10 	| x_3 	| y_n 	| .. 	| .. 	| x_5 	| -->

<!-- Ordered: Permuting from the same levels -->

<!-- | facets/observation     	| 1  	| 2  	| 3  	| .. 	| .. 	| n  	| -->
<!-- |-----	|------	|------	|------	|----	|----	|------	| -->
<!-- | B_1 	| x_3 	| x_10 	| x_100 	| .. 	| .. 	| x_1 	| -->
<!-- | B_2 	| y_n 	| y_2 	| y_10 	| .. 	| .. 	| y_3 	| -->
<!-- | B_3 	|      	|      	|      	|    	|    	|      	| -->
<!-- | ..  	|      	|      	|      	|    	|    	|      	| -->
<!-- | ..  	|      	|      	|      	|    	|    	|      	| -->
<!-- | B_L 	| z_10 	| z_200 	| z_10 	| .. 	| .. 	| z_5 	| -->

```{r}
sm <- smart_meter10 %>%
filter(customer_id %in% c(10017936))
.data = sm
sm %>% prob_plot("week_month", "day_week", plot_type = "boxplot")

sm %>% prob_plot("day_month", "hour_day", plot_type = "quantile", symmetric = FALSE, quantile_prob = c(0.05, 0.25, 0.5, 0.75, 0.95))

# Results

##  Smart meter data

normal: standard normal ordered distances  
normal_nonstd: non-standard normal ordered distances  
normal_un: standard normal unordered distances  
normal_nonstd_un: non-standard normal unordered   distances

```{r allgraph}
library(readr)
smart_normal <- read_rds("data/ smart_harmony_normal.rds")  %>% mutate(rank_normal = row_number())

smart_normal_nonstd <- read_rds("data/smart_harmony_nonstd.rds") %>% mutate(rank_normal_nonstnd = row_number())

smart_normal_un <- read_rds("data/smart_harmony_normal_unordered.rds")  %>% mutate(rank_normal_un = row_number())

smart_normal_nonstd_un <- read_rds("data/smart_harmony_nonstd_unordered.rds") %>% mutate(rank_normal_nonstnd_un = row_number())

smart_normal %>% 
  left_join(smart_normal_nonstd, by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>% 
   rename("normal" = "mean_max_variation.x", "normal_nonstd" = "mean_max_variation.y") %>%

  left_join(smart_normal_un, by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>% 
  rename("normal_un" = "mean_max_variation") %>%

  left_join(smart_normal_nonstd_un, by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>% 
  rename("normal_nonstd_un" = "mean_max_variation")%>% select(-c(normal, normal_nonstd, normal_un, normal_nonstd_un))%>%
  dplyr::rename("normal"  = "rank_normal",
         "normal_nonstd"  = "rank_normal_nonstnd",
         "normal_un"  = "rank_normal_un",
         "normal_nonstd_un"  = "rank_normal_nonstnd_un")%>%   knitr::kable(format = "latex")
```

<!-- # unordered -->

<!-- ```{r} -->
<!-- library(readr) -->
<!-- smart_normal <- read_rds("data/smart_harmony_normal_unordered.rds")  %>% mutate(rank_normal = row_number()) -->

<!-- smart_normal_nonstd <- read_rds("data/smart_harmony_nonstd_unordered.rds") %>% mutate(rank_normal_nonstnd = row_number()) -->

<!-- smart_normal %>%  -->
<!--   left_join(smart_normal_nonstd, by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>%  -->
<!--    rename("normal" = "mean_max_variation.x", "normal_nonstd" = "mean_max_variation.y") %>%  -->
<!--   select(-c(normal, normal_nonstd))%>% -->
<!--   dplyr::rename("normal_unordered"  = "rank_normal", -->
<!--          "normal_nonstd_unordered"  = "rank_normal_nonstnd")%>%   knitr::kable(format = "latex") -->
<!-- ``` -->

## Graphical evidence

```{r, echo = FALSE}
smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>%
  prob_plot("wknd_wday",
    "hour_day",
    response = "general_supply_kwh",
    plot_type = "boxplot",
    #symmetric = TRUE,
    #quantile_prob = c(0.01, 0.1, 0.25, 0.5, 0.75, 0.9, 0.99)
  ) +
  scale_y_sqrt() +
  #ggtitle(" (b) Area quantile plot faceted by weekend-weekday") +
  ylab("electricity demand [KWh]") + xlab("hours of the day") + ggtitle("") + ylab("")+ 
  theme_minimal() + 
  scale_x_discrete(breaks = seq(0, 23, 5))

smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>% prob_plot( gran1 = "day_week", gran2 = "day_month", plot_type = "boxplot") + scale_x_discrete(breaks = seq(0, 31, 5))

smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>% prob_plot(gran1 = "wknd_wday", gran2 = "day_month", plot_type = "boxplot") + scale_x_discrete(breaks = seq(0, 31, 5))

smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>% 
  prob_plot(gran1 = "wknd_wday", gran2 = "hour_day", plot_type = "boxplot")

smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>%
  prob_plot("hour_day",
    "wknd_wday",
    response = "general_supply_kwh",
    plot_type = "boxplot",
    #symmetric = TRUE,
    #quantile_prob = c(0.01, 0.1, 0.25, 0.5, 0.75, 0.9, 0.99)
  ) +
  scale_y_sqrt() +
  #ggtitle(" (b) Area quantile plot faceted by weekend-weekday") +
  ylab("electricity demand [KWh]") + xlab("") + ggtitle("") + ylab("")+ 
  theme_minimal() + scale_x_discrete(labels = c('wday','wend'))

>>>>

---
title: Finalised versions of normalisation and threshold
authors:
- name: Sayani Gupta
  affiliation: Department of Econometrics and Business Statistics, Monash University
  email: Sayani.Gupta@monash.edu

@@

# Does normalisation work?
(Show with by comparing with maximum and showing for similar levels)

@@

@@

**Assumption:** random permutation without considering ordering 
(global)

@@

# Does it match with the threshold?
# Should they tally with each other?
